Methods for Large Scale Learning to Rank

### 2014-03-13 report/Chapters/Background.tex
verwerking self-check

%************************************************
This chapter provides a background in the Learning-to-Rank field with the goal of making the subsequential chapters of this thesis understandable for non-experts in the field.
\section{A basic introduction to Learning-to-Rank}
Different definitions of Learning-to-Rank exist. In general, all ranking methods that use machine learning technologies to solve the problem of ranking are called Learning-to-Rank methods. Figure \ref{fig:discriminative_training} describes the general process of machine learning. It shows training elements from an input space that are mapped to an output space using a model such that the difference between the actual labels of the training elements and the labels predicted with with the model are minimal in terms of a loss function.
\begin{figure}[!h]
\includegraphics[scale=0.26]{gfx/descriminative_training}
\caption{Machine learning framework for Learning-to-Rank, obtained from Liu \cite{Liu2007}}
\label{fig:discriminative_training}
\end{figure}\\
Liu \cite{Liu2007} proposes a more narrow definition and only considers ranking methods to be a Learning-to-Rank method when it is \emph{feature based} and uses \emph{discriminative training}, which are itself defined as follows:
\begin{description}
\item[Feature Based]{means that all documents under investigation are represented by feature vectors. Those feature vectors reflect the relevance of the documents to the query, or the importance of the document in itself.}
\item[Discriminative Training]{means that the learning process can be well described by the four components of discriminative learning. That is, a Learning-to-Rank method has its own \emph{input space}, \emph{output space}, \emph{hypothesis space}, and \emph{loss function}, like the machine learning process described by Figure \ref{fig:discriminative_training}. \emph{Input space}, \emph{output space}, \emph{hypothesis space}, and \emph{loss function} are hereby defined as follows:
	\begin{description}
	\item[Input Space]{contains the objects under investigation. Usually objects are represented by feature vectors, extracted according to different applications.}
	\item[Output Space]{contains the learning target with respect to the input objects.}
	\item[Hypothesis Space]{defines the class of functions mapping the input space to the output space. The functions operate on the feature vectors of the input object, and make predictions according to the format of the output space.}
	\item[Loss Function]{in order to learn the optimal hypothesis, a training set is usually used, which contains a number of objects and their ground truth labels, sampled from the product of the input and output spaces.}
	\end{description}
	}
\end{description}

@@

\section{Evaluating a ranking}
Evaluation metrics have long been studied in the field of information retrieval. First in the form of evaluation of unranked retrieval sets and later, when the information retrieval field started focussing more on ranked retrieval, in the form of ranked retrieval evaluation. In this section several frequently used evaluation metrics for ranked results will be described.\\

@@

Well-known algorithms that belong to the listwise approach include AdaRank \cite{Xu2007}, BoltzRank \cite{Volkovs2009}, ListMLE \cite{Xia2008}, ListNet \cite{Cao2007}, RankCosine \cite{Qin2008}, SmoothRank \cite{Chapelle2010}, SoftRank \cite{Taylor2008}, SVM$^map$ \cite{Yue2007}.

>>>>

%************************************************
This chapter is written with the goal to provide the reader with a subtle introduction in the Learning-to-Rank field. Models and theories explained in this chapter can be regarded as prior knowledge needed to understand the subsequent chapters of this thesis.
\section{A basic introduction to Learning-to-Rank}
Different definitions of Learning-to-Rank exist. In general, all ranking methods that use machine learning technologies to solve the problem of ranking are called Learning-to-Rank methods. Figure \ref{fig:discriminative_training} describes the general process of machine learning. It shows training elements from an input space that are mapped to an output space using a model such that the difference between the actual labels of the training elements and the labels predicted with with the model are minimal in terms of a loss function.
\begin{figure}[!h]
\includegraphics[scale=0.26]{gfx/descriminative_training}
\caption{Machine learning framework for Learning-to-Rank, obtained from Liu \cite{Liu2007}}
\label{fig:discriminative_training}
\end{figure}\\
Liu \cite{Liu2007} proposes a more narrow definition and only considers ranking methods to be a Learning-to-Rank method when it is \emph{feature based} and uses \emph{discriminative training}, which are itself defined as follows:
\begin{description}
\item[Feature Based]{means that all documents under investigation are represented by feature vectors. Those feature vectors reflect the relevance of the documents to the query, or the importance of the document in itself.}
\item[Discriminative Training]{means that the learning process can be well described by the four components of discriminative learning. That is, a Learning-to-Rank method has its own \emph{input space}, \emph{output space}, \emph{hypothesis space}, and \emph{loss function}, like the machine learning process described by Figure \ref{fig:discriminative_training}. \emph{Input space}, \emph{output space}, \emph{hypothesis space}, and \emph{loss function} are hereby defined as follows:
	\begin{description}
	\item[Input Space]{contains the objects under investigation. Usually objects are represented by feature vectors, extracted according to different applications.}
	\item[Output Space]{contains the learning target with respect to the input objects.}
	\item[Hypothesis Space]{defines the class of functions mapping the input space to the output space. The functions operate on the feature vectors of the input object, and make predictions according to the format of the output space.}
	\item[Loss Function]{in order to learn the optimal hypothesis, a training set is usually used, which contains a number of objects and their ground truth labels, sampled from the product of the input and output spaces.}
	\end{description}
	}
\end{description}

@@

\section{How to evaluate a ranking}
Evaluation metrics have long been studied in the field of information retrieval. First in the form of evaluation of unranked retrieval sets and later, when the information retrieval field started focussing more on ranked retrieval, in the form of ranked retrieval evaluation. In this section several frequently used evaluation metrics for ranked results will be described.\\

@@

Well-known algorithms that belong to the listwise approach include AdaRank \cite{Xu2007}, BoltzRank \cite{Volkovs2009}, ListMLE \cite{Xia2008}, ListNet \cite{Cao2007}, RankCosine \cite{Qin2008}, SmoothRank \cite{Chapelle2010}, SoftRank \cite{Taylor2008}, SVM$^{map}$ \cite{Yue2007}.

### 2014-03-13 report/Chapters/Introduction.tex
verwerking self-check

\section{Approach}
A literature study will be performed to get insight in relevant existing techniques for large scale Learning-to-Rank. The literature study will be performed by using the following query:
\begin{itemize}
\item ("learning to rank" OR "learning-to-rank" OR "machine learned ranking") AND ("parallel" OR "distributed")
\end{itemize}
and the following bibliographic databases:
\begin{itemize}
\item Scopus
\item Web of Science
\end{itemize}

@@

\begin{description}
\item[Chapter II: Background]{introduces the reader to the basic principles and recent work in the fields of Learning-to-Rank.}
\item[Chapter III: Related Work]{concisely describes existing work in the field of parallel machine learning and parallel Learning-to-Rank.}
\item[Chapter IV: Benchmark Results]{sketches the accuracy of existing Learning-to-Rank methods on several benchmark datasets and describes the selection of Learning-to-Rank methods for the parallelisation experiments.}
\item[Chapter V: Selected Learning-to-Rank Methods]{describes the algorithms and details of the Learning-to-Rank methods selected in Chapter IV.}
\item[Chapter VI: Implementation]{describes implementation details of the Learning-to-Rank algorithms in the Hadoop framework.}
\item[Chapter VII: Results \& Discussion]{presents and discusses speed-up results for the implemented Learning-to-Rank methods.}
\item[Chapter VIII: Conclusion]{summarizes the results and answers our research questions based on the results. The limitations of our research as well as future research directions in the field are mentioned here.}
\end{description}

>>>>

\section{Approach}
A literature study will be performed to get insight in relevant existing techniques for large scale Learning-to-Rank. The literature study will be performed by using the following query:\\

\emph{("learning to rank" \emph{OR} "learning-to-rank" \emph{OR} "machine learned ranking") \emph{AND} ("parallel" \emph{OR} "distributed")}\\

and the following bibliographic databases:
\begin{itemize}
\item Scopus
\item Web of Science
\item Google Scholar
\end{itemize}

@@

\begin{description}
\item[Chapter II: Background]{introduces the reader to the basic principles and recent work in the fields of Learning-to-Rank.}
\item[Chapter III: Related Work]{concisely describes existing work in the field of parallel Learning-to-Rank.}
\item[Chapter IV: Benchmark Results]{sketches the accuracy of existing Learning-to-Rank methods on several benchmark datasets and describes the selection of Learning-to-Rank methods for the parallelisation experiments.}
\item[Chapter V: Selected Learning-to-Rank Methods]{describes the algorithms and details of the Learning-to-Rank methods selected in Chapter IV.}
\item[Chapter VI: Implementation]{describes implementation details of the Learning-to-Rank algorithms in the Hadoop framework.}
\item[Chapter VII: Results \& Discussion]{presents and discusses speed-up results for the implemented Learning-to-Rank methods.}
\item[Chapter VIII: Conclusion]{summarizes the results and answers our research questions based on the results. The limitations of our research as well as future research directions in the field are mentioned here.}
\end{description}

### 2014-03-13 report/Chapters/RelatedWork.tex
forward reference search verwerkt
verwerking self-check

\section{Literature study characteristics}
The literature research is performed by using the bibliographic databases Scopus and Web of Science with the following search query: \emph{("learning to rank" OR "learning-to-rank" OR "machine learned ranking") AND ("parallel" OR "distributed")}. An abstract based manual filtering step is applied where I filter those results that actually use the \emph{parallel} or \emph{distributed} terms in context to the \emph{learning to rank}, \emph{learning-to-rank} or \emph{machine learned ranking}. Studies focusing on efficient query evaluation instead of efficient model training are likely to meet all criteria listed. As a last step I will filter out studies based on the whole document that only focus on efficient query evaluation and not on parallel or distributed learning of ranking functions.\\

on Scopus the defined search query resulted in 65 documents. Only 14 of those documents used \emph{large scale}, \emph{parallel} or \emph{distributed} terms in context to the \emph{learning to rank}, \emph{learning-to-rank} or \emph{machine learned ranking}. 10 out of those 14 documents focussed on parallel or distributed learning of ranking functions.\\

The defined search query resulted in 16 documents on Web of Science. Four of those documents were also present in the set of 65 documents found using Scopus, leaving 61 unique documents. Only four of those 61 documents used \emph{large scale}, \emph{parallel} or \emph{distributed} terms in context to the \emph{learning to rank}, \emph{learning-to-rank} or \emph{machine learned ranking}, none of them focussed on parallel or distributed learning of ranking functions.\\

On Google Scholar the defined search query resulted in 3300 documents. We evaluate the first 300 search results.\\

A one-level forward and backward reference search is used to find relevant papers missed so far. To handle the large volume of studies involved in the backward and forward reference search, relevance of the studies will be evaluated solely on the title of the study. Backward reference search resulted in 10 studies regarded as potentially relevant based on the title of which four were actually relevant and included in the literature description. Forward reference search resulted in 10 potentially relevant titles, of which x studies turned out to be relevant.\\

Research in large scale Learning-to-Rank model training can be categorised according to the approach that they take in scaling up the training step of Learning-to-Rank models. Figure \ref{fig:related_work_categories} illustrates the categories of scalable training approaches in Learning-to-Rank. The following sections describe the related work in the field following the categorisation depicted in Figure \ref{fig:related_work_categories}.

@@

\section{Parallelising Learning-to-Rank through ensemble learning}
Schapire proved in 1990 that a strong model can be generated by combining weak models through a procedure that he called boosting \cite{Schapire1990}. The invention of the boosting method resulted in an increasing focus in machine learning research on methods to combine multiple weak models, which are called ensemble learning methods. Well-known ensemble methods include gradient boosting \cite{Friedman2001}, bagging \cite{Breiman1996}, AdaBoost \cite{Freund1997} and stacked generalisation (stacking) \cite{Wolpert1992}.\\

Ensemble methods can be used to parallelise learning methods by training the weak models in the ensemble on different nodes. In the Learning-to-Rank field parallelisation of model training through ensemble learning is frequently achieved using decision tree learners and often using the boosting ensemble method, jointly called \acf{GBDT}. \ac{GBDT}'s are shown to be able to achieve good accuracy in a Learning-to-Rank setting when used in a pairwise \cite{Zheng2007} or listwise \cite{Chen2008} setting.

@@

Kocsis et al. \cite{Kocsis2013} propose way to train multiple weak learners in parallel by extending those models that are likely to yield a good model when combined through boosting. Authors showed through theoretical analysis that the proposed algorithm asymptotically achieve equal performance to regular gradient boosting. \ac{GBDT} models could be trained in parallel using their BoostingTree algorithm.\\

Tyree et al. \cite{Tyree2011} describe a way of parallelising \ac{GBDT} models for Learning-to-Rank where the boosting step is still executed sequentially, instead the construction of the regression trees themselves are parallelised. The parallel decision tree building is based on Ben-Haim and Yom-Tov's work on parallel construction of decision trees for classification \cite{Ben-Haim2010}. Decision trees are build layer-by-layer where the calculations needed for building each new layer in the tree are divided over the nodes using a master-worker paradigm. The data is partitioned of the workers, who compress their share into histograms and send these to the master. The master uses those histograms to approximate the split and build the next layer. The master than communicates this new layer to the workers who can use this new layer to compute new histograms. this process is repeated until the tree depth limit is reached. The tree construction algorithm parallelised with described master-worker method is \ac{CART} \cite{Breiman1984}. Speed-up experiments on the LETOR and the Yahoo! Learning to Rank challenge data sets were performed. This parallel \ac{CART}-tree building approach showed speed-up of up to 42x on shared memory machines and up to 25x on distributed memory machines.\\

@@

\section{Learning-to-Rank parallelisation by hardware acceleration}
Hardware accelerators are special purpose processors designed to speed up compute-intensive tasks. An \ac{FPGA} and a \ac{GPU} are two different types of hardware that can achieve better performance on some tasks though parallel computing. In general, \ac{FPGA}s provide better performance while \ac{GPU}s tend to be easier to program \cite{Che2008}. Some research has been done in parallelising Learning-to-Rank methods using hardware accelerators.

@@

\section{Parallelised execution of algorithm steps in Learning-to-Rank methods}
Some research focused on parallelising the steps Learning-to-Rank algorithms that can be characterised as strong learners.
\subsection{Parallel ListNet using Spark}
Shukla et al. \cite{Shukla2012} explored the parallelisation of the well-known ListNet Learning-to-Rank method using Spark. Spark is a parallel computing model that is designed for cyclic data flows which makes it more suitable for iterative algorithms. Spark is incorporated into Hadoop since Hadoop 2.0. The Spark implementation of ListNet showed near a linear training time reduction.\\

@@

\section{Parallelisable Search Heuristics for Listwise ranking}
Direct minimisation of ranking metrics is a hard problem due to the non-continuous, non-differentiable and non-convex nature of \ac{nDCG}, \ac{ERR} and \ac{MAP}. This optimisation problem is generally addressed either by replacing the ranking metric with a convex surrogate, or by heuristic optimisation methods such as Simulated Annealing or a \ac{EA}. One \ac{EA} heuristic optimisation method that is successfully used in direct rank evaluation functions optimisation is the \ac{GA} \cite{Yeh2007}. \ac{GA}s are search heuristic functions that mimic the process of natural selection, consisting of mutation and cross-over steps \cite{Holland1995}. The following subsection describe related work that uses search heuristics for parallel/distributed training.
\subsection{Immune Programming}
Wang et al. \cite{Wang2009b} proposed a \ac{IP} solution to direct ranking metric optimisation and observed that all \ac{EA}s are generally easy to implement such that it can be carried out on different computers distributively. However, no statements on the possible speed-up of a distributed implementation of the \ac{IP} solution has been made and no speed-up experiments have been conducted.
\subsection{CCRank}
Wang et al. \cite{Wang2011a,Wang2011b} propose a parallel evolutionary algorithm based on \ac{CC}, a type of evolutionary algorithm. The \ac{CC} algorithm is capable of directly optimizing non-differentiable functions, as \ac{nDCG}, in contrary to many optimization algorithms.  the divide-and-conquer nature of the \ac{CC} algorithm enables parallelisation. CCRank showed an increase in both accuracy and efficiency on the LETOR 4.0 benchmark dataset compared to the baselines. It must be stated however that the increased efficiency was achieved through speed-up and not scale-up. Two reasons have been identified for not achieving linear scale-up with CCRank: 1) parallel execution is suspended after each generation to perform combination in order to produce the candidate solution, 2) Combination has to wait until all parallel tasks have finished, which may spend different running time.
\subsection{nDCG-Annealing}
Karimzadeghan et al. \cite{Karimzadehgan2011} proposed a method using Simulated Annealing along with the Simplex method for its parameter search. This method directly optimises the often non-differentiable Learning-to-Rank evaluation metrics like \ac{nDCG} and \ac{MAP}. The authors successfully parallelised their method in the MapReduce paradigm using Hadoop. The approach showed to be effective on both the LETOR 3.0 dataset and their own dataset with contextual advertising data. Unfortunately their work does not directly report on the speed-up obtained by parallelising  with Hadoop, but it is mentioned that further work needs to be done to effectively leverage parallel execution.\\

@@

Another \ac{ADMM} Learning-to-Rank based approach was proposed by Boyd et al. \cite{Boyd2012}. Boyd et al. \cite{Boyd2012} implemented an \ac{ADMM} based Learning-to-Rank method in Pregel \cite{Malewicz2010}, a parallel computation framework for graph computations. No experimental results on parallelisation speed-up were reported on this Pregel based approach.
\subsection{Learning-to-Rank with Bregman Divergences and Monotone Retargeting}
Acharyya et al. \cite{Acharyya2012, Acharyya2013} propose a Learning-to-Rank method searches for an order preserving transformation (\emph{monotone retargeting}) of the target scores that is easier for a regressor to fit. This approach is based on the observation that it is not necessary to fit scores exactly, since the evaluation is dependent on the order and not on the pointwise predictions themselves.\\

@@

\section{Distributed Hyperparameter Tuning using MapReduce}
Ganjisaffar et al. \cite{Ganjisaffar2011, Ganjisaffar2011b} observed that long training times are often a result of training many models for hyperparameter optimisation. Grid search is the \emph{de facto} standard of hyperparameter optimisation and is simply an exhaustive search through a manually specified subset of hyperparameter combinations. The authors show how to perform parallel grid search on MapReduce clusters, which is easy because grid search is an embarrassingly parallel method as hyperparameter combinations are mutually independent. They apply their grid search on MapReduce approach in a Learning-to-Rank setting to train a LambdaMART \cite{Wu2008} ranking model, a model that uses the Gradient Boosting \cite{Friedman2002} ensemble method combined with regression tree weak learners. Experiments showed that the solution scales linearly in number of hyperparameter combinations. However, the risk of overfitting grows overwhelmingly as the number of hyperparameter combinations grow, even when validation sets grow large.\\

>>>>

\section{Literature study characteristics}
The literature research is performed by using the bibliographic databases Scopus and Web of Science with the following search query:\\

\emph{("learning to rank" \emph{OR} "learning-to-rank" \emph{OR} "machine learned ranking") \emph{AND} ("parallel" \emph{OR} "distributed")}\\

An abstract-based manual filtering step is applied where those results are filtered that use the terms \emph{parallel} or \emph{distributed} in context to \emph{learning to rank}, \emph{learning-to-rank} or \emph{machine learned ranking}. As a last step I will filter out studies based on the whole document that only focus on efficient query evaluation and not on parallel or distributed learning of ranking functions, as those studies are likely to meet listed search terms.\\

On Scopus, the defined search query resulted in 65 documents. Only 14 of those documents used \emph{large scale}, \emph{parallel} or \emph{distributed} terms in context to the \emph{learning to rank}, \emph{learning-to-rank} or \emph{machine learned ranking}. 10 out of those 14 documents focussed on parallel or distributed learning of ranking functions.\\

The defined search query resulted in 16 documents on Web of Science. Four of those documents were part of the 10 relevant documents found using Scopus, leaving 12 new potentially relevant documents to consider. Four of those 12 documents used \emph{large scale}, \emph{parallel} or \emph{distributed} terms in context to the \emph{learning to rank}, \emph{learning-to-rank} or \emph{machine learned ranking}, none of them focused on parallel or distributed learning of ranking functions.\\

On Google Scholar, the defined search query resulted in 3300 documents. Because it infeasible to evaluate all 3300 studies we focus on the first 300 search results.\\

Backward reference search resulted in 10 studies regarded as potentially relevant based on the title of which four were actually relevant and included in the literature description. Forward reference search resulted in 10 potentially relevant titles, of which seven studies turned out to be relevant.\\

Research in scaling up the training phase of Learning-to-Rank models can be categorised according to the approach in scaling up. Figure \ref{fig:related_work_categories} illustrates the categories of scalable training approaches in Learning-to-Rank. The following sections describe the related work in the field following this categorisation.

@@

\section{Ensemble learning for parallel Learning-to-Rank}
Schapire proved in 1990 that a strong model can be generated by combining weak models through a procedure that he called boosting \cite{Schapire1990}. The invention of the boosting method resulted in an increasing focus in machine learning research on methods to combine multiple weak models, which are called ensemble learning methods. Well-known ensemble methods include gradient boosting \cite{Friedman2001}, bagging \cite{Breiman1996}, AdaBoost \cite{Freund1997} and stacked generalisation (often called stacking) \cite{Wolpert1992}.\\

Ensemble methods can be used to parallelise learning methods by training the weak models in the ensemble on different nodes. In the Learning-to-Rank field parallelisation of model training through ensemble learning is frequently achieved using decision tree learners and often using the boosting ensemble method, jointly called \acf{GBDT}. \ac{GBDT}s are shown to be able to achieve good accuracy in a Learning-to-Rank setting when used in a pairwise \cite{Zheng2007} or listwise \cite{Chen2008} setting.

@@

Kocsis et al. \cite{Kocsis2013} propose a way to train multiple weak learners in parallel by extending those models that are likely to yield a good model when combined through boosting. Authors showed through theoretical analysis that the proposed algorithm asymptotically achieve equal performance to regular gradient boosting. \ac{GBDT} models could be trained in parallel using their BoostingTree algorithm.\\

@@

\section{Hardware accelerated Learning-to-Rank}
Hardware accelerators are special purpose processors designed to speed up compute-intensive tasks. An \ac{FPGA} and a \ac{GPU} are two different types of hardware that can achieve better performance on some tasks though parallel computing. In general, \ac{FPGA}s provide better performance while \ac{GPU}s tend to be easier to program \cite{Che2008}. Some research has been done in parallelising Learning-to-Rank methods using hardware accelerators.

@@

\section{Parallelisation through execution of algorithm steps in Learning-to-Rank methods}
Some research focused on parallelising the steps Learning-to-Rank algorithms that can be characterised as strong learners.

Tyree et al. \cite{Tyree2011} describe a way of parallelising \ac{GBDT} models for Learning-to-Rank where the boosting step is still executed sequentially and instead the construction of the regression trees themselves is parallelised. The parallel decision tree building is based on Ben-Haim and Yom-Tov's work on parallel construction of decision trees for classification \cite{Ben-Haim2010}. Decision trees are build layer-by-layer where the calculations needed for building each new layer in the tree are divided over the nodes using a master-worker paradigm. The data is partitioned of the workers, who compress their share into histograms and send these to the master. The master uses those histograms to approximate the split and build the next layer. The master than communicates this new layer to the workers who can use this new layer to compute new histograms. this process is repeated until the tree depth limit is reached. The tree construction algorithm parallelised with described master-worker method is \ac{CART} \cite{Breiman1984}. Speed-up experiments on the LETOR and the Yahoo! Learning to Rank challenge data sets were performed. This parallel \ac{CART}-tree building approach showed speed-up of up to 42x on shared memory machines and up to 25x on distributed memory machines.\\

\subsection{Parallel ListNet using Spark}
Shukla et al. \cite{Shukla2012} explored the parallelisation of the well-known ListNet Learning-to-Rank method using Spark. Spark is a parallel computing model that is designed for cyclic data flows which makes it more suitable for iterative algorithms. Spark is incorporated into Hadoop since Hadoop 2.0. The Spark implementation of ListNet showed near a linear training time reduction.\\

@@

\section{Parallelisable search heuristics for Listwise ranking}
Direct minimisation of ranking metrics is a hard problem due to the non-continuous, non-differentiable and non-convex nature of \ac{nDCG}, \ac{ERR} and \ac{MAP}. This optimisation problem is generally addressed either by replacing the ranking metric with a convex surrogate, or by heuristic optimisation methods such as Simulated Annealing or a \ac{EA}. One \ac{EA} heuristic optimisation method that is successfully used in direct rank evaluation functions optimisation is the \ac{GA} \cite{Yeh2007}. \ac{GA}s are search heuristic functions that mimic the process of natural selection, consisting of mutation and cross-over steps \cite{Holland1995}. The following subsection describe related work that uses search heuristics for parallel/distributed training.
\subsection{Immune Programming}
Wang et al. \cite{Wang2009b} proposed a \ac{IP} solution to direct ranking metric optimisation and observed that all \ac{EA}s are generally easy to implement such that it can be carried out on different computers distributively. However, no statements on the possible speed-up of a distributed implementation of the \ac{IP} solution has been made and no speed-up experiments have been conducted.
\subsection{CCRank}
Wang et al. \cite{Wang2011a,Wang2011b} propose a parallel evolutionary algorithm based on \ac{CC}, a type of evolutionary algorithm. The \ac{CC} algorithm is capable of directly optimizing non-differentiable functions, as \ac{nDCG}, in contrary to many optimization algorithms.  the divide-and-conquer nature of the \ac{CC} algorithm enables parallelisation. CCRank showed an increase in both accuracy and efficiency on the LETOR 4.0 benchmark dataset compared to the baselines. It must be stated however that the increased efficiency was achieved through speed-up and not scale-up. Two reasons have been identified for not achieving linear scale-up with CCRank: 1) parallel execution is suspended after each generation to perform combination in order to produce the candidate solution, 2) Combination has to wait until all parallel tasks have finished, which may spend different running time.
\subsection{nDCG-Annealing}
Karimzadeghan et al. \cite{Karimzadehgan2011} proposed a method using Simulated Annealing along with the Simplex method for its parameter search. This method directly optimises the often non-differentiable Learning-to-Rank evaluation metrics like \ac{nDCG} and \ac{MAP}. The authors successfully parallelised their method in the MapReduce paradigm using Hadoop. The approach showed to be effective on both the LETOR 3.0 dataset and their own dataset with contextual advertising data. Unfortunately their work does not directly report on the speed-up obtained by parallelising  with Hadoop, but it is mentioned that further work needs to be done to effectively leverage parallel execution.\\

@@

Another \ac{ADMM} Learning-to-Rank based approach was proposed by Boyd et al. \cite{Boyd2012}. Boyd et al. \cite{Boyd2012} implemented an \ac{ADMM} based Learning-to-Rank method in Pregel \cite{Malewicz2010}, a parallel computation framework for graph computations. No experimental results on parallelisation speed-up were reported on this Pregel based approach.
\subsection{Bregman Divergences and Monotone Retargeting}
Acharyya et al. \cite{Acharyya2012, Acharyya2013} propose a Learning-to-Rank method searches for an order preserving transformation (\emph{monotone retargeting}) of the target scores that is easier for a regressor to fit. This approach is based on the observation that it is not necessary to fit scores exactly, since the evaluation is dependent on the order and not on the pointwise predictions themselves.\\

@@

\section{Distributed hyperparameter tuning using MapReduce}
Ganjisaffar et al. \cite{Ganjisaffar2011, Ganjisaffar2011b} observed that long training times are often a result of training many models for hyperparameter optimisation. Grid search is the \emph{de facto} standard of hyperparameter optimisation and is simply an exhaustive search through a manually specified subset of hyperparameter combinations. The authors show how to perform parallel grid search on MapReduce clusters, which is easy because grid search is an embarrassingly parallel method as hyperparameter combinations are mutually independent. They apply their grid search on MapReduce approach in a Learning-to-Rank setting to train a LambdaMART \cite{Wu2008} ranking model, a model that uses the Gradient Boosting \cite{Friedman2002} ensemble method combined with regression tree weak learners. Experiments showed that the solution scales linearly in number of hyperparameter combinations. However, the risk of overfitting grows overwhelmingly as the number of hyperparameter combinations grow, even when validation sets grow large.\\
